---
title: "Discrete Distributions: Binomial and Poisson"
output: pdf_document
---

## Binomial Distriution

Consider a sample of n infants with a 0.06 probability of developing asthma. Calculate the probability that exactly 5 infants develop asthma.

```{r}
# n = 5
dbinom(5, 20, 0.06)

# n = 100
dbinom(5, 100, 0.06)

```

Now, calculate the probability that at least 10 infants have asthma from a sample of 20.

P(X >= 10) = 1 - P(X <= 9)

```{r}

1 - pbinom(9, 20, 0.06)

```

Create a function to graph the binomial distribution with parameters n and p.

```{r}
# define function
bin_graph = function(n, p) {
  
  x = dbinom(0:n, size = n, prob = p)
  barplot(x, names.arg = 0:n)
  
}

# call function
bin_graph(n = 20, p = 0.06)
bin_graph(n = 100, p = 0.06)
bin_graph(n = 100, p = 0.5)

```

## Poisson Distribution

Let lambda be the rate (number of calls per hour).

Calculate the probability of having exactly 4 calls in the next hour for lambda = 10.

```{r}

dpois(4, 10)

```

Calculate the probability of receiving at most 8 calls in one hour.

```{r}

ppois(8, 10)

```

What does the Poisson distribution look with with different lambdas?

```{r}
# define domain
x = 0:20

# lambda = 3
plot(x, dpois(x, 3), type = "h", ylim = c(0,0.25),
     xlab = "x", ylab = "P(x)", main = "Lambda = 3")

# lambda = 5
plot(x, dpois(x, 5), type = "h", ylim = c(0,0.25),
     xlab = "x", ylab = "P(x)", main = "Lambda = 5")

# lambda = 10
plot(x, dpois(x, 10), type = "h", ylim = c(0,0.25),
     xlab = "x", ylab = "P(x)", main = "Lambda = 10")

```

## Excersize 

Assume a rare birth defect occurs with probability 0.0001 and we collect a sample of 4,000 babies. Calculate the probability of having at least 10 babies with a birth defect.

Note: this probability can be computed using either the binomial or Poisson distribution.

```{r}
# binomial
1 - pbinom(9, 4000, 0.0001)

# Poisson 
1 - ppois(9, 0.4)

```

Both probabilities are approximately 0.











